\begin{abstract}
Crowdsourced entity extraction is often used to acquire data for many applications, including recommendation systems, 
construction of aggregated listings and directories, and knowledge base compilation. Current solutions focus on entity extraction using a single query, e.g., only using `give me another restaurant', when assembling a list of all restaurants. Due to the time and cost of human labor, just focusing on a single query limits the practical applicability of these solutions.

In this paper, we leverage a {\em structured entity domain}, i.e., domains that can be fully described by a collection of attributes, each potentially displaying hierarchical structure. Given such an entity domain, we enable a richer space of queries, e.g., `give me another Moroccan restaurant in Manhattan that does takeout'. Naturally, enabling a richer space of queries comes with a host of issues, especially since many queries return empty answers. We develop new statistical tools that enable users to reason about the gain of issuing {\em additional queries} in the presence of little to no information, and show how we can exploit the dependencies across different points of the data
domain to obtain accurate estimates of the gain. We demonstrate that for the problem of {\em budgeted entity extraction} over large domains, we can cast it as an adaptive optimization problem that seeks to maximize the number of extracted entities, while minimizing the overall extraction costs. We evaluate our techniques with experiments on both synthetic and real-world datasets, demonstrating a yield of up to XXX over competing approaches for the same budget.

% Crowd entity extraction has become a popular means of acquiring data for many applications, including recommendation systems, listing aggregation and knowledge base compilation.  Most of the current solutions focus on entity extraction for specific queries and do not consider entity extraction over broader entity domains. Due to the time and cost of human labor, considering each query in isolation may incur large costs when applied to broader domains, thus, limiting the applicability of current approaches.
 
% In this paper, we explore the problem of {\em budgeted entity extraction} over {\em structured entity domains}. We consider domains that can be fully described by a collection of attributes, each characterized by a hierarchical structure. We develop new statistical tools that enable users to reason about the gain of issuing {\em further queries} in the presence of little information and show how to exploit the dependencies across different points of the data domain to obtain more accurate estimates. We also demonstrate how budgeted entity extraction over large domains can be cast as an adaptive optimization problem that seeks to maximize the number of extracted entities while minimizing the overall extraction cost. We evaluate our techniques with experiments on both synthetic and real-world data. 
\end{abstract}
